Distribution-oblivious Programming with Dish

### 2019-10-02 pldi/draft.tex
Update intro

Distributed systems offer significant benefits over their centralized counterparts.
For example, they can speed up computations and can process amounts that would not fit into any single machine.
% offer notable benefits over their centralized counterparts:
%   using partitioning and replication, they can process and store data with increased throughput and fault-tolerance.
% Yet, only a minority of developers, employed by the select few companies that deal with massive datasets, have the luxury of engineering software systems with distribution baked in from the start.
% The remaining majority starts by developing and deploying software in a centralized manner---that is, \emph{until} there is a significant change of requirements, such as a load increase.

Despite these benefits, their development remains different from and significantly more difficult than their centralized counterparts.
Whereas anyone can stitch together a Bash script to compute on a single computer, 
  % domain-experts routinely glue scripts together to process and share data. % without the help of a computing expert.
   scaling out to multiple ones requires expert labor around ``point'' solutions with expensive setups, restricted programming interfaces, and exorbitant composition costs~\cite{taurus:14, dios:13, andromeda:2015, pywren:17, futuredata:18, nefele:18}.

@@

\heading{Identifiers}
The file-system is a common abstraction layer used for many other operations than just serving files (this will be become clearer when talking about file-system commands in \S\ref{bg:cmd}).
as such, different identifiers many not resolve to actual files, but rather in-memory or OS-internal structures.

>>>>

Distributed systems offer significant benefits over their centralized counterparts---for example, they can speed up expensive computations or process data that would not fit into any single machine.
% offer notable benefits over their centralized counterparts:
%   using partitioning and replication, they can process and store data with increased throughput and fault-tolerance.
% Yet, only a minority of developers, employed by the select few companies that deal with massive datasets, have the luxury of engineering software systems with distribution baked in from the start.
% The remaining majority starts by developing and deploying software in a centralized manner---that is, \emph{until} there is a significant change of requirements, such as a load increase.
Despite these benefits, their development remains different from and significantly more difficult than their centralized counterparts.
Whereas anyone can quickly stitch together a Bash script to compute on a single computer, 
  % domain-experts routinely glue scripts together to process and share data. % without the help of a computing expert.
   scaling out to multiple ones requires expert labor around ``point'' solutions with expensive setups, restricted programming interfaces, and exorbitant composition costs~\cite{taurus:14, dios:13, andromeda:15, pywren:17, futuredata:18, nefele:18}.

@@

\heading{Identifiers}

The file-system is a common abstraction layer used for many other operations than just serving files (this will be become clearer when talking about file-system commands in \S\ref{bg:cmd}).
as such, different identifiers many not resolve to actual files, but rather in-memory or OS-internal structures.
